$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/paper.tex
Remove incorrect claim

\subsection{Contributions}
Our contributions are the following:
\begin{itemize}
\item \textbf{Formalisation of the syntax and semantics of the \picalc{}}:
  Section \S \ref{syntax} uses type level de Bruijn indices \cite{} to introduce a syntax that is well-scoped by construction: every free variable is accounted for in the type of the process that uses it.
  Section \S \ref{semantics} provides an operational semantics for the untyped \picalc{}, prior to any typing.
  This operational semantics is given as a reduction relation on processes.
  The reduction relation tracks at the type level what channel the communication occurs on, so that this information can then be used to state subject reduction --- ak-a type preservation.
  It is also defined modulo structural congruence --- a relation that acts as a quotient type that gets rid of the unecessary syntactic minutiae introduced by the syntax of the \picalc{}.

@@

Structural congruence is a congruent equivalence relation on processes.
Any two structurally congruent processes are strongly bisimilar: they are can follow each other's reduction steps \cite{}.
Figure \ref{fig:struct-cong-base} lists the base cases of structural congruence.
The type $\Unused_i \; Q$ is an inductive proof that witnesses that the variable index $i$ does not appear nor in the inputs nor in the outputs of $Q$.
The function $lower_i \; Q \; uQ$ traverses $Q$ decrementing every index bigger than $i$.
Finally, $swap_i \; P$ traverses $P$ (of type $\Process_{\suc \suc n}$) and swaps variable references $i$ and $\suc i$.
In all three, $i$ is incremented every time we go under a binder.

>>>>

\subsection{Contributions}
Our contributions are the following:
\begin{itemize}
\item \textbf{Formalisation of the syntax and the semantics of the \picalc{}}:
  Section \S \ref{syntax} uses type level de Bruijn indices \cite{} to introduce a syntax that is well-scoped by construction: every free variable is accounted for in the type of the process that uses it.
  Section \S \ref{semantics} provides an operational semantics for the untyped \picalc{}, prior to any typing.
  This operational semantics is given as a reduction relation on processes.
  The reduction relation tracks at the type level what channel the communication occurs on, so that this information can then be used to state subject reduction --- ak-a type preservation.
  It is also defined modulo structural congruence --- a relation that acts as a quotient type that gets rid of the unecessary syntactic minutiae introduced by the syntax of the \picalc{}.

@@

Structural congruence is a congruent equivalence relation on processes.
Figure \ref{fig:struct-cong-base} lists the base cases of structural congruence.
The type $\Unused_i \; Q$ is an inductive proof that witnesses that the variable index $i$ does not appear nor in the inputs nor in the outputs of $Q$.
The function $lower_i \; Q \; uQ$ traverses $Q$ decrementing every index bigger than $i$.
Finally, $swap_i \; P$ traverses $P$ (of type $\Process_{\suc \suc n}$) and swaps variable references $i$ and $\suc i$.
In all three, $i$ is incremented every time we go under a binder.
